\section{Related Work}
\label{sec:related}

\paragraph{LLM-based and automated peer review.}
The prospect of using large language models to assist scholarly peer review has
moved rapidly from speculation to systematic study. The most influential
empirical anchor is the large-scale analysis of \citet{liang2024llm}, who
compared GPT-4 feedback against human reviews across thousands of Nature-family
and ICLR papers and found that the overlap between model and human comments was
comparable to the overlap between two human reviewers. Complementary pilot and
exploratory studies reached more tempered conclusions: \citet{robertson2023gpt4}
characterized GPT-4 as ``slightly helpful'' for review assistance, and
\citet{liu2023reviewergpt} showed that targeted prompting (e.g., asking the model
to find a specific error) substantially outperforms asking it to write a
free-form review, while also exposing brittleness on deliberately injected
errors. A second strand engineers multi-agent or pipeline architectures to
overcome context limits and genericness: MARG \citep{darcy2024marg} distributes a
paper across specialized agents to cut generic comments and raise specificity,
and the AI Scientist \citep{lu2024aiscientist} embeds an automated reviewer
inside an end-to-end discovery loop. More recent work turns a critical lens on
the paradigm itself, with \citet{du2024llmsassist} building the ReviewCritique
dataset to surface deficiencies in machine-written reviews and
\citet{zhou2024reliable} documenting that high agreement on identified strengths
and weaknesses does not translate into reliable decision prediction. The
ecosystem-level risk is captured by \citet{russolatona2024lottery}, who estimate
that AI-assisted reviews already inflate scores and acceptance probabilities at
scale, and by \citet{lin2025hidden}, who documents adversarial hidden prompts
embedded in manuscripts that manipulate AI-assisted reviews outright---risks that
make uncontrolled, undisclosed AI use in review a live concern. On the constructive
side, a large-scale randomized controlled study at ICLR~2025
\citep{thakkar2026feedback} deployed an LLM feedback agent to over 20{,}000 reviews
and found that automated feedback measurably improved review informativeness and
reviewer--author engagement. Crucially, almost all of this work---including these
interventions---evaluates generated review \emph{text} rather than a calibrated
numeric \emph{score}.

\paragraph{Reliability and noise in the human ground truth.}
Any claim that an automated signal tracks ``quality'' must be calibrated against
the known unreliability of the human ground truth it is compared to. The NeurIPS
consistency experiments are the canonical evidence: \citet{cortes2021inconsistency}
revisited the 2014 experiment and \citet{beygelzimer2023arbitrary} replicated it
at larger scale in 2021, both finding that roughly half of accepted papers would
change under a re-run of the process, and that review largely succeeds at
rejecting weak papers but struggles to rank strong ones. This asymmetry directly
motivates the deliberately narrow claim of our study. The reliability literature
also documents systematic bias, including affiliation-driven inflation under
single-blind review \citep{tomkins2017reviewerbias} and the statistical
subtleties of testing for such bias \citep{stelmakh2019biases};
\citet{shah2022challenges} provides the integrative survey.

\paragraph{Datasets, benchmarks, and validation methodology.}
The computational study of peer review rests on a now-mature set of resources.
PeerRead \citep{kang2018peerread} established the first public corpus pairing
drafts with reviews and decisions and introduced the acceptance-prediction task;
AMPERE \citep{hua2019argument} added argument-level structure, and NLPeer
\citep{dycke2023nlpeer} contributed an ethically sourced, multi-venue
unification. \citet{yuan2022automate} trained and evaluated review-generation
models and concluded the technology was not ready for high-stakes settings, while
the Dagstuhl-derived survey \citep{kuznetsov2024whatcan} sets the field's current
agenda. On validation methodology for noisy, ordinal ground truth, the literature
converges on rank correlation \citep{spearman1904}, paired-comparison modeling of
ordinal outcomes \citep{bradley1952}, threshold-free discrimination via AUROC,
and explicit calibration assessment \citep{guo2017calibration};
\citet{checco2021aiassisted} is a direct precedent for validating a learned score
against acceptance decisions and reviewer ratings, albeit with a neural text
classifier rather than an LLM. Because citation count is a tempting but
treacherous quality proxy, our secondary citation analysis is framed by
\citet{aksnes2019citations} and \citet{tahamtan2016factors}, which document the
field, age, and venue confounds that make citations a lagging, contaminated
signal.

\paragraph{Positioning.}
Our contribution differs along three axes. First, we validate a structured LLM
\emph{score}---five 0--100 dimensions plus an overall---against two complementary
ground truths simultaneously (discrete decision tiers and continuous reviewer
ratings), rather than judging the prose quality of generated review \emph{text}
\citep{liang2024llm,darcy2024marg,yuan2022automate}. Second, we adopt the
validation discipline the prior literature largely omits: pre-registered
hypotheses and metrics, chosen because the human signal is demonstrably noisy and
ordinal \citep{cortes2021inconsistency,beygelzimer2023arbitrary}. Third, our
claim is deliberately bounded---the score consistently flags weak submissions and
correlates with human outcomes, without predicting acceptance or replacing
reviewers---mirroring the ``good at rejecting, poor at ranking'' asymmetry, and we
report failure modes rather than headlining best-case overlap.
