\section{Conclusion}
\label{sec:conclusion}

We validated a structured LLM paper-scoring system against the public decisions
and reviewer ratings of a major machine learning venue, under a pre-registered,
fully reproducible protocol. The score separates rejected from accepted
submissions (AUROC~$\aurocMini$), rises monotonically across decision tiers, and
correlates with continuous reviewer ratings ($\rho=\spearmanRatingMini$). The
signal is strongest at the low end: weak submissions are consistently flagged,
with the lowest score quintile rejected at \bottomRejectRateFrontier\% on the
production model (\bottomRejectRate\% at scale on the cheap-model cohort), a lift
over base rate with strong work absent from that band. We confirmed the effect on a frontier-model cohort and showed that a cheap
model proxies the frontier score well enough to establish the relationship at
scale. The study's central result is about the model rather than the pipeline. A generic
one-paragraph prompt on the same model and PDF already separates rejected from
accepted submissions (AUROC~\aurocNaive), and the structured rubric-and-audit
pipeline discriminates no better (the paired difference is not statistically
significant): with or without our prompt, a frontier model already produces a
first-pass reviewing signal that substantially tracks human outcomes in this cohort,
so raw model intelligence is not the observed bottleneck, and the reviewer keeps the
decision. What the engineered pipeline
adds is not a higher score but a deployable one---grading far more consistently
across repeated runs and returning a grounded, anchored review in the same pass.

Pre-registering the claim, validating against two complementary ground truths,
generating every number from the data, and cataloguing the failure modes together
keep the result inside the boundary the evidence supports: an automated first pass that reliably
surfaces weak work for human attention, not a replacement for the judgment that
follows. That boundary follows the reliable-at-the-bottom asymmetry the human
process itself exhibits.

\paragraph{Reproducibility.}
The de-identified scored table, the decision and rating labels, the analysis
code, and the pre-registration are released; \texttt{run\_all.py} regenerates
every figure, table, and number in this paper from the data with a single
command. The full generated review text for identifiable submissions is not
published by default; it is retained as a controlled audit artifact for editors
or reviewers if needed. The grading rubric, prompts, and model configuration
remain proprietary; the manuscript-to-score function is audited through its
outputs rather than re-implemented.
