% ===========================================================================
% Cover letter — Nature Machine Intelligence submission. One page.
% Standalone: compiles on its own. Build:  pdflatex cover_letter_nmi.tex
% TODO before sending:
%   [ ] Confirm article type (Analysis vs Article).
%   [ ] Add suggested / opposed reviewers (comment below the signature).
%   [ ] Pin exact competing-interest wording (ownership / equity / patents).
% ===========================================================================
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.85in]{geometry}
\usepackage[colorlinks=true,allcolors=blue]{hyperref}
\usepackage{parskip}
\setlength{\parskip}{2pt plus 1pt}
\pagestyle{empty}

\newcommand{\myname}{Costa Georgantas}
\newcommand{\papertitle}{Intelligence Is Not the Bottleneck: Validating an LLM
  First-Pass Manuscript Score Against Peer-Review Outcomes}

\begin{document}

\noindent
\myname\\
Independent Researcher, Lausanne, Switzerland\\
\href{mailto:costa.georgantas@gmail.com}{costa.georgantas@gmail.com} \quad
ORCID: \href{https://orcid.org/0009-0008-8891-4582}{0009-0008-8891-4582}

\smallskip
\noindent\today

\smallskip
\noindent The Editors, \textit{Nature Machine Intelligence}

\smallskip
\noindent Dear Editors,

I submit ``\papertitle'' for consideration as an \textbf{Analysis}. % TODO: or Article

Large language models are increasingly used to assist peer review, yet evaluations judge the
text a model writes, not the validity of the numeric score it assigns, the signal a flagging
use depends on. I validate AIPR, a prompt-only manuscript scorer, against
the public OpenReview record of a major machine-learning venue that publishes its rejected
submissions, so the reject class my central claim concerns is fully observable.

The contribution is twofold and, to my knowledge, new. First, this is the first validation of
a training-free, prompt-only manuscript-quality score against a real venue's reject class and
mean reviewer ratings, with hypotheses pre-registered before any score met any outcome. Second,
it decomposes, against those outcomes, where the score's value comes from: a bare one-paragraph
prompt on the same model already carries most of the discriminative signal, and what the
engineered pipeline adds is reliability, not sharper discrimination. I do not claim to introduce
score stabilization, which is established (self-consistency, ensembling, rubric conditioning),
nor the reliability-versus-validity distinction, which recent work documents in other settings;
the contribution is bringing that discipline to peer review, validating a prompt-only score
against a real venue's reject class and reviewer ratings under pre-registration.

I am candid about evidentiary weight. The validity is pre-registered and strong (AUROC 0.87 on
the production model, 0.82 replicated on 300 papers, rising across decision tiers). The
pipeline's discrimination advantage over the bare prompt is not statistically resolved at the
sample size I committed to in advance ($n=100$; $p=0.09$), and I report it as such. The
statistically clear result is reliability: the production score barely moves across repeated
gradings of the same manuscript (within-paper SD 0.7 vs.\ 2.8 points for the bare prompt;
Wilcoxon $p=0.014$). AIPR is human-in-the-loop; every part of the review, including the passage
highlights on the manuscript, is editable.

I have a declared stake: I founded and operate AIPR
(\href{https://aipr.pub}{aipr.pub}), the commercial system evaluated here. The safeguards are
structural: the analysis plan was frozen at a public pre-registration tag before any score met
any outcome, the scores, labels, and code are openly released
(\href{https://github.com/cogeor/aipr-score-validation}{github.com/cogeor/aipr-score-validation};
\href{https://doi.org/10.5281/zenodo.21105072}{Zenodo}) and regenerate every figure, and the
primary comparison includes a baseline built to make my own pipeline redundant. The proprietary
scorer is validated through its outputs, with prompts available confidentially to editors and
reviewers. AI tools assisted drafting; I verified all content and take responsibility, as
disclosed in the manuscript. A preprint is on arXiv (Creative Commons); an interactive companion
is at \href{https://aipr.pub/publications}{aipr.pub/publications}; I have had no prior editorial
discussions.

I am glad to strengthen the study during revision, most usefully by grading more manuscripts to
resolve the pipeline-versus-prompt comparison, adding a temporal replication on an adjacent ICLR
year, or discussing release of the prompts. The manuscript is my own work as sole author and is
not under consideration elsewhere.

Thank you for considering it.

\smallskip
\noindent Sincerely,\\[0.3em]
\myname

% TODO reviewers (cover letter is not seen by referees):
% Suggested, none with a conflict: (1) ..., (2) ..., (3) ...
% Opposed, with reason: ...

\end{document}
