% ===========================================================================
% Score-validation study — Nature Machine Intelligence (Analysis) variant.
% Doc-to-doc translation of the arXiv manuscript: the SAME section files, reordered to the
% NMI main-text sequence (Introduction -> Results -> Discussion -> Methods/Data), with the
% arXiv appendix reused verbatim as Supplementary Information. Only the abstract is bespoke
% (frontier headline + 150-word cap). Prose and figure placement track the arXiv build.
% Build:  python cli.py paper --nmi   (run analysis first to populate macros)
% Title is intentionally identical to main.tex (kept per author decision).
% ===========================================================================
\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{xspace}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage[numbers,sort&compress]{natbib}
\PassOptionsToPackage{hyphens}{url}
\usepackage[colorlinks=true,allcolors=blue]{hyperref}
\usepackage{caption}
\captionsetup{font=small,labelfont=bf}
\usepackage{microtype}

\graphicspath{{figures/}}

% --- numbers from the analysis (override the placeholders below) -----------
\IfFileExists{macros/results_macros.tex}{\input{macros/results_macros.tex}}{}
\IfFileExists{macros/sim_macros.tex}{\input{macros/sim_macros.tex}}{}
\IfFileExists{macros/secondary_macros.tex}{\input{macros/secondary_macros.tex}}{}
\input{macros.tex} % \providecommand defaults; fills any gap so the doc always builds

% \anonymousfalse => named exemplars, matching the arXiv build (main.pdf); the reused
% arXiv sections carry the same named case studies.
\newif\ifanonymous\anonymousfalse
\IfFileExists{ANONYMOUS.flag}{\anonymoustrue}{}
% Relocate heavy detail (e.g. the scoring formula) to the SI for the NMI length budget,
% while the arXiv build keeps it inline. Used by the shared arXiv section files.
\newif\ifnmibuild\nmibuildtrue

\title{\textbf{Intelligence Is Not the Bottleneck:\\
Validating an LLM First-Pass Manuscript Score Against Peer-Review Outcomes}}

\author{%
  Costa Georgantas\\
  Independent Researcher, Lausanne, Switzerland\\
  \texttt{\small costa.georgantas@gmail.com}\\
  ORCID: \href{https://orcid.org/0009-0008-8891-4582}{0009-0008-8891-4582}%
}
\date{}

\begin{document}
\maketitle

% A loud, removable banner whenever the build is on synthetic data.
\IfFileExists{macros/SYNTHETIC.flag}{%
  \begin{center}\fcolorbox{red}{red!8}{\parbox{0.9\linewidth}{\centering
  \textcolor{red}{\textbf{DRAFT ON SYNTHETIC DATA.} All numbers and figures below
  are generated from \texttt{synth.py} for formatting verification only and are
  not results. Re-run \texttt{run\_all.py} against the real export to populate.}}}\end{center}
}{}

\input{sections/nmi_00_abstract}

% arXiv section files, reused verbatim, reordered to the NMI sequence. Figure placement is
% arXiv's: the study-design and validation figures live in the SI (09_appendix), not here.
\input{sections/01_introduction}  % folds 02_related_work inline (NMI majority style)
\input{sections/05_results}
\input{sections/06b_discussion}
\input{sections/03_data}
\input{sections/04_methods}

% --- End-of-paper statements (Nature Portfolio required sections) -----------
\section*{Data availability}
The data supporting the findings of this study are openly available at
\url{https://github.com/cogeor/aipr-score-validation} and permanently archived at
\url{https://doi.org/10.5281/zenodo.21105072}, anchored to the pre-registration tag
\texttt{prereg-iclr2026-v2}. The release contains the two-table contract every analysis
reads: per-submission labels (decision tier, mean reviewer rating) and per-grading-run
scores, keyed by public OpenReview submission identifiers. All decision outcomes, ratings,
and review excerpts derive from the public OpenReview record of ICLR~2026
(\texttt{ICLR.cc/2026/Conference}) under CC~BY~4.0; we redistribute only derived metadata and
our own scores, not manuscript PDFs or full review texts. The full AIPR review text for
identifiable submissions is a controlled audit artifact available to editors and reviewers on
request.

\section*{Code availability}
All analysis code needed to reproduce the study is openly available at
\url{https://github.com/cogeor/aipr-score-validation} and permanently archived at
\url{https://doi.org/10.5281/zenodo.21105072}; a single command regenerates every figure,
table, and statistic in this paper and its Supplementary Information from the released data. The
manuscript-to-score function evaluated here (AIPR's grading rubric, prompts, and model
configuration) is a proprietary production system and is not released as source.
Consistent with its role as the validated instrument, it is audited through its outputs and
can be exercised on new manuscripts via \url{https://aipr.pub}, with the rubric, prompts, and
configuration made available confidentially to editors, reviewers, or auditors on request.
Because the analysis plan was pre-registered before unblinding, this arrangement lets the
validation be checked independently even though the scorer itself is closed.

\section*{Competing interests}
The author founded and operates AIPR (\url{https://aipr.pub}), the commercial system evaluated
in this study, and stands to benefit from a favourable result. The study was self-funded; no
external funding was received. The mitigations are structural rather than rhetorical: the
analysis plan was frozen at a public tag before any score was joined to an outcome, every
reported number regenerates from released code and data, and the primary comparison includes
a baseline designed to make the pipeline redundant.

\bibliographystyle{plainnat}
\bibliography{refs}

% Supplementary Information: the full technical record reused from the canonical
% appendix (pre-registration, schema, robustness suite, failure-mode case studies).
\appendix
\renewcommand{\appendixname}{Supplementary Information}

\section{Scoring formula}
The overall AIPR score is the fixed weighted mean of the five dimension scores (novelty,
rigor, applicability, clarity, citation),
\begin{equation}
  \text{overall} = \frac{4\,s_{\text{nov}} + 2\,s_{\text{rig}}
  + 4\,s_{\text{app}} + 1\,s_{\text{cla}} + 0.5\,s_{\text{cit}}}{11.5},
  \label{eq:overall}
\end{equation}
with novelty and applicability weighted most and citation least. The weights were set by
internal validation on a held-out manuscript set and frozen before this study, not fit to
any outcome used here.

\input{sections/09_appendix}
\input{sections/06_failure_modes}
\input{sections/07_limitations}

\end{document}
